FoRTE baseline

### 2019-01-31 analysis/paper/paper.Rmd
PAPER: Start `ed-notes` doc. Update references, fix typos.

- Finite canopy radius (`CROWN_MOD`)
    - Options:
        - (0; default): Complete shading
        - (1): Finite canopy radius (Dietze 2008)
    - See current hypotheses
- Nitrogen limitation of photosynthesis (`N_PLANT_LIM`)
    - Options:
        - (0, default): No limitation
        - (1) Limitation based on internal model (TODO: what is it?)
    - Turning this on _should_ favor mid-successional species, and substantially increase uncertainty.
- Nitrogen limitation of decomposition (`N_PLANT_LIM`)
    - Options:
        - (0, default): No limitation
        - (1) Limitation based on internal model (TODO: what is it?)
    - Same as above

>>>>

- Finite canopy radius (`CROWN_MOD`)
    - Options:
        - (0; default): Complete shading
        - (1): Finite canopy radius (Dietze 2008)
    - See current hypotheses
    - This model is based on @dietze_2008_capturing
- Nitrogen limitation of photosynthesis (`N_PLANT_LIM`)
    - Options:
        - (0, default): No limitation
        - (1) Limitation based on internal model (TODO: what is it?)
    - Turning this on _should_ favor mid-successional species, and substantially increase uncertainty.
- Nitrogen limitation of decomposition (`N_DECOMP_LIM`)
    - Options:
        - (0, default): No limitation
        - (1) Limitation based on internal model (TODO: what is it?)
    - Same as above
